% Options for packages loaded elsewhere
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
  ignorenonframetext,
]{beamer}
\newif\ifbibliography
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% remove section numbering
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{section title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{subsection title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}

\usetheme[]{Copenhagen}
\usecolortheme[]{whale}
\usefonttheme[]{structurebold}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother


\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
\usepackage{caption}
% Make caption package work with longtable
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother


% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}



\setlength{\emergencystretch}{3em} % prevent overfull lines

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}



 


\setbeamertemplate{items}[circle]
\setbeamertemplate{footline}[frame number]
\usepackage{setspace}
\setbeamerfont{title}{size=\large}
\setbeamerfont{author}{size=\large}
\setbeamerfont{institute}{size=\small}
\setbeamerfont{date}{size=\small}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Discussion: Industry-specific effects of geopolitical risk on the volatility of the Johannesburg Stock Exchange: A GARCH-MIDAS approach},
  pdfauthor={Xolani Sibande},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}


\title{Discussion: Industry-specific effects of geopolitical risk on the
volatility of the Johannesburg Stock Exchange: A GARCH-MIDAS approach}
\subtitle{Finstab Research Symposium: Maintaing financial stability amid
global volatility and uncertainty}
\author{Xolani Sibande}
\date{2025-06-24}
\institute{South African Reserve Bank}

\begin{document}
\frame{\titlepage}


\begin{frame}[s]{Purpose}
\phantomsection\label{purpose}
\setstretch{1.5}

\begin{itemize}
\tightlist
\item
  A focus on the effect of geopolitical risk (GPR) on the volatility of
  industry returns in the Johannesburg Stock Exchange (JSE)
\item
  Particularly, industry-specific effects for 9 sector indexes
  (e.g.~financials, health, industrials, etc.)
\item
  Using the popular Caldara and Iacoviello
  (\citeproc{ref-caldara2022measuring}{2022}) GPR index
\item
  Applied GARCH-MIDAS (mixed data frequency) approach
\item
  Briefly, the paper aims to understand how GPR shocks affect the
  volatility of industry returns
\end{itemize}
\end{frame}

\begin{frame}[s]{Key findings}
\phantomsection\label{key-findings}
\setstretch{1.5}

\begin{itemize}
\tightlist
\item
  Finding 1: Confirmed a industry effect
\item
  Finding 2: Only the healthcare index showed a higher return volatility
  due to GPR shocks
\item
  Finding 3: The rest demonstrated lower volatility response
\item
  Finding 4: Similar global and local GPR effects
\end{itemize}
\end{frame}

\begin{frame}[s]{Comment 1: Strenghs}
\phantomsection\label{comment-1-strenghs}
\setstretch{1.5}

\begin{itemize}
\tightlist
\item
  Well presented paper
\item
  Consideration of the literature
\item
  Careful implementation of the GARCH-MIDAS approach (not common)
\end{itemize}
\end{frame}

\begin{frame}[s]{Comment 2: Centrality of investor behaviour}
\phantomsection\label{comment-2-centrality-of-investor-behaviour}
\setstretch{1.4}

\begin{itemize}
\tightlist
\item
  Why study industry effect in the first place?

  \begin{itemize}
  \tightlist
  \item
    We expect investors to \textbf{react} differently to GPR shocks
    across industries
  \end{itemize}
\item
  What does it mean for investors to react differently?

  \begin{itemize}
  \tightlist
  \item
    It means that investors can overreact to information
    (\citeproc{ref-de1985does}{De Bondt and Thaler 1985})
  \item
    It means that investors substitute private information for market
    information (\citeproc{ref-devenow1996rational}{Devenow and Welch
    1996})
  \item
    It means that investors may have different risk preferences across
    industries (\citeproc{ref-plastun2020halloween}{Plastun et al.
    2020})
  \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[s]{Comment 2: Centrality of investor behaviour cont.}
\phantomsection\label{comment-2-centrality-of-investor-behaviour-cont.}
\setstretch{1.5}

\begin{itemize}
\tightlist
\item
  The literature has shown in differentiated industry impact in other
  areas (for example, \citeproc{ref-sibande2024presidential}{Sibande et
  al. 2024})
\item
  Lastly the debate on the literature as to the centrality of investor
  behaviour of investor behaviour is largely settled
  (\citeproc{ref-fakhry2016literature}{Fakhry 2016})
\item
  The paper does not take a clear stand on the investor behaviour aspect
\end{itemize}
\end{frame}

\begin{frame}[s]{Comment 3: Volatility is difficult to explain}
\phantomsection\label{comment-3-volatility-is-difficult-to-explain}
\setstretch{1.5}

\begin{itemize}
\tightlist
\item
  Volatility is difficult to explain because it is non-linear
\item
  More returns volatility is not necessarily better or worse (not
  necessarily indicative of crises)
\item
  Markets have become more \textbf{efficient} over time
  (\citeproc{ref-plastun2019rise}{Plastun et al. 2019})
\item
  In addition the concept of GPR can be difficult to pin down
  (e.g.~wars, elections, etc.)
\item
  For robustness, the paper could have considered other measures of GPR
  or specific events (crises periods)
\item
  Therefore, difficult to draw policy conclusions
\end{itemize}
\end{frame}

\begin{frame}[s]{Comment 4: Understanding volatility is important for
financial stability}
\phantomsection\label{comment-4-understanding-volatility-is-important-for-financial-stability}
\setstretch{1.5}

\begin{itemize}
\tightlist
\item
  However, understanding the drivers of volatility is important for
  financial stability
\item
  It can be helpful to first understand the effect of returns volatility
  on real economic variables, for example employment
  (\citeproc{ref-sibande2019time}{Sibande, Gupta, and Wohar 2019})
\item
  Then from the decomposition of volatility, short and long term policy
  implications can be drawn
\item
  That is, in addition, the paper could have considered the effect of
  GPR shocks on real economic variables
\end{itemize}
\end{frame}

\begin{frame}{Conclusion}
\phantomsection\label{conclusion}
\center

\large Great paper - beneficial area of work for EMs!
\end{frame}

\begin{frame}[allowframebreaks]{References}
\phantomsection\label{references}
\small
\setstretch{0}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-caldara2022measuring}
Caldara, Dario, and Matteo Iacoviello. 2022. {``Measuring Geopolitical
Risk.''} \emph{American Economic Review} 112 (4): 1194--1225.

\bibitem[\citeproctext]{ref-de1985does}
De Bondt, Werner FM, and Richard Thaler. 1985. {``Does the Stock Market
Overreact?''} \emph{The Journal of Finance} 40 (3): 793--805.

\bibitem[\citeproctext]{ref-devenow1996rational}
Devenow, Andrea, and Ivo Welch. 1996. {``Rational Herding in Financial
Economics.''} \emph{European Economic Review} 40 (3-5): 603--15.

\bibitem[\citeproctext]{ref-fakhry2016literature}
Fakhry, Bachar. 2016. {``A Literature Review of the Efficient Market
Hypothesis.''} \emph{Turkish Economic Review} 3 (3): 431--42.

\bibitem[\citeproctext]{ref-plastun2019rise}
Plastun, Alex, Xolani Sibande, Rangan Gupta, and Mark E Wohar. 2019.
{``Rise and Fall of Calendar Anomalies over a Century.''} \emph{The
North American Journal of Economics and Finance} 49: 181--205.

\bibitem[\citeproctext]{ref-plastun2020halloween}
---------. 2020. {``Halloween Effect in Developed Stock Markets: A
Historical Perspective.''} \emph{International Economics} 161: 130--38.

\bibitem[\citeproctext]{ref-sibande2024presidential}
Sibande, Xolani, Vassilios Babalos, Riza Demirer, and Rangan Gupta.
2024. {``Presidential Politics and Investor Behavior in the Stock
Market: Evidence from a Century of Stock Market Data.''}

\bibitem[\citeproctext]{ref-sibande2019time}
Sibande, Xolani, Rangan Gupta, and Mark E Wohar. 2019. {``Time-Varying
Causal Relationship Between Stock Market and Unemployment in the United
Kingdom: Historical Evidence from 1855 to 2017.''} \emph{Journal of
Multinational Financial Management} 49: 81--88.

\end{CSLReferences}
\end{frame}




\end{document}
